Capstone Movielens Report

### 2025-11-24 reports/capstone-movielens.site/05.appendix.Rmd
Hotfix for functioin: Function described: regularize.test_lambda.UM_effect.cv.

Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* in the *regularization process*.

@@

This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
:::

>>>>

Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* in the *regularization process* using the *penalized approach* with use of *K-Fold Cross-Validation*.

@@

This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: {.noteblock data-latex=""}
We choose `K = 5`in *This Project*.
:::
:::
